\sectionTitle{Projects}{\faIcon{code}}
\textbf{\large{Thesis}}\\
My thesis consisted of selecting the stars most likely to host habitable planets, and identify those whose conditions make it difficult to detect the presence of any planets. From this work, a set of criteria for identifying probable planet-hosting stars, and a tool for measuring the how badly a star's atmosphere can effect the measurement required to detect a planet. 
\begin{itemize}
    \item Querying online databases.
    \item Cross-matching subsets of multiple databases.
    \item Quantitative analysis.
    \item Coding of scripts to perform analysis.
\end{itemize}
\,\\
\textbf{\large{Classification of stars}}\\
Modern technologies allow for the observation of hundred to thousands of stars simultaneously. however, analysis needs to keep to a similar pace. Previously stars were classified manually and one at a time. Machine learning offers the opportunity to classify at a greater pace and without human intervention. This is a complex task as the parameters required for classification vary across star types. This work looked at the measurements obtained by the GALAH survey (www.galah-survey.org/) for 588K stars to determine if any of the parameters were useful in predicting classes of star.
\begin{itemize}
    \item Data cleaning and preparation.
    \item Feature engineering.
    \item Model selection and training.
    \item Hyperparameter tuning.
\end{itemize}
\,\\
\textbf{\large{House price regression}}\\
This project was part of a public competition, hosted by Kaggle (www.kaggle.com), to predict the selling price of houses in Ames, Iowa, U.S.A. using regression techniques. The dataset contained 79 features, such as the number of bathrooms, the size of the basement, and the suburb the house was located at. The dataset is notable for having a significant number of missing entries across a number of columns, which require thorough data cleaning to shape the data into a form suitable for regression.
\begin{itemize}
    \item Analysis of missing entries.
    \item Feature engineering.
    \item Target transformation.
    \item Comparison of models.
\end{itemize}